Language-Based Security for Low-Level MPC

### 2024-05-17 ppdp24/intro.tex
checkpoint

Various related low-level languages with probabilistic features have
also been developed. The $\lambda_{\mathrm{obliv}}$ language
\cite{darais2019language} uses a type system is used to automatically
enforce so-called probabilistic trace obliviousness.  But similar to
previous work on oblivious data structures \cite{10.1145/3498713},
obliviousness is related to pure noninterference, not the relaxed form
related to passive MPC security. The Haskell-based security type system in
\cite{6266151} enforces a version of conditioned noninterence that is
sound for passive security in a probabilisitic low-level setting, but
they do not consider malicious security. And properties of real/ideal
passive and malicious security for a probabilistic language have been
formulated in EasyCrypt \cite{8429300}-- though their proof methods,
while mechanized, are fully manual, and their formulation of malicious
security is not as clearly related to robust declassification as the
one we present in Section \ref{section-hyperprop}.

>>>>

Various related low-level languages with probabilistic features have
also been developed. The $\lambda_{\mathrm{obliv}}$ language
\cite{darais2019language} uses a type system is used to automatically
enforce so-called probabilistic trace obliviousness.  But similar to
previous work on oblivious data structures \cite{10.1145/3498713},
obliviousness is related to pure noninterference, not the relaxed form
related to passive MPC security. The Haskell-based security type system in
\cite{6266151} enforces a version of conditioned noninterence that is
sound for passive security in a probabilisitic low-level setting, but
they do not consider malicious security. And properties of real/ideal
passive and malicious security for a probabilistic language have been
formulated in EasyCrypt \cite{8429300}-- though their proof methods,
while mechanized, are fully manual, and their formulation of malicious
security is not as clearly related to robust declassification as is the
one we present in Section \ref{section-hyper}.
